\section{Introduction}

Software development has grown to a point, where we have a giant base of great
algorithms, that enable us to solve many problems quickly and efficiently. In
todays software development it often comes down to having an idea and
implementing it on the basis of these existing algorithms. Still there is a
limit to what they can do and it is often reached at tasks that seem pretty
simple to us humans. Algorithms are great in using big amounts of data,
accumulating it to models and trends, showing it in smart graphs, generating
visual representations and simplifying the analysis and interpretation. Still
the final interpretation is a skill where humans are unmatched in, until now.
\newline
These days, more and more companies are starting to implement machine learning
(ML) algorithms as support to their existing algorithms. These ML algorithms are
the closest a program can come to the human ability to use experience and learn
from it, in order to interpret new experiences on the basis of the old ones.
While they have been around for a while now, it has not yet got to a reliability
to be established as standard. As the topic becomes more and more important in
todays world, getting to know it, can prove very valuable in the future.
\newline
This paper follows the entire process of creating a so called "artificial
intelligence" that is able to take an image, grabbed from a file or a video and
determine, if showing a person, which kind of mask this person is wearing or
whether he/she is wearing any at all. First the project and its goals will be
layed out in detail with a short introduction of each team member and their role
in this project. This is followed by a description of the used dataset and how
it was created. Then there will be an outline of the process including used
methodologies and encountered difficulties and finally a summarization of the
obtained results and their interpretation. 